MULTI process challenge : the FML solution

### 2021-03-12 1-Main.tex

%\documentclass[preprint]{acmart}
\documentclass[preprint]{elsarticle}
\journal{EMISA Journal}

@@

@@

@@

\begin{document}
\begin{frontmatter}

\title{MULTI process challenge : the FML solution}

@@

%% or include affiliations in footnotes:
\author[mymainaddress]{Sylvain Guérin\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mymainaddress]{Joel Champeau}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author[mysecondaryaddress]{Jean-Christophe Bach}
%\ead{firstname.lastname@imt-atlantique.fr}

\author[mysecondaryaddress]{Salvador Mart\'inez}
%\ead{firstname.lastname@imt-atlantique.fr}

\author[mysecondaryaddress]{Antoine Beugnard}
%\ead{firstname.lastname@imt-atlantique.fr}

\address[mymainaddress]{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}%vérifier si c'est l'affiliation officielle
\address[mysecondaryaddress]{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}

\input{2-Abstract}

\begin{keyword}
Multilevel modeling \sep Challenge
\end{keyword}

\end{frontmatter}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

@@

\end{document}
\endinput
%%

>>>>

%\documentclass[preprint]{acmart}
\documentclass[american]{emisa}

@@

\newcommand{\noteSM}[1]{\todo[color=red!40, author=\textbf{Salvador}, inline, caption={}]{#1}}
\newcommand{\noteJC}[1]{\todo[color=blue!40, author=\textbf{JC}, inline, caption={}]{#1}}
\newcommand{\noteSylvain}[1]{\todo[color=green!40, author=\textbf{Sylvain}, inline, caption={}]{#1}}
\newcommand{\noteAntoine}[1]{\todo[color=yellow!40, author=\textbf{Antoine}, inline, caption={}]{#1}}

@@

\usepackage{amsmath,amssymb,mathtools}
\usepackage{algorithmic,algorithm}

@@

\begin{document}
\begin{article}{
\title{MULTI process challenge : the FML solution}

@@

%% or include affiliations in footnotes:
\author*{Sylvain Guérin}{firstname.lastname@ensta-bretagne.fr}
\address{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}
%\ead{firstname.lastname@ensta-bretagne.fr}

\author{Joel Champeau}
\address[a]{}

\author{Jean-Christophe Bach}
\address{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}
%\ead{firstname.lastname@imt-atlantique.fr}

\author{Salvador Mart\'inez}
\address[b]{}

\author{Antoine Beugnard}
\address[b]{}

\abstract{\input{2-Abstract}}
\keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
\bibliography{}
}
%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

\noteSM{teste}
\noteJC{test}
\noteSylvain{Test}
\noteAntoine{Test}

@@

\end{article}
\end{document}
\endinput
%%
